\documentclass[a4paper]{article}
%\usepackage[T1]{fontenc}
%\usepackage{mathptmx}
\usepackage{gentium}

\usepackage[top=.5in, bottom=.5in, left=.5in, right=.5in]{geometry}
\makeatletter
\@ifundefined{KOMAClassName}{
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{
    \KOMAoptions{parskip=half}% if KOMA class
}

\makeatother
\usepackage{longtable,booktabs,array}
\usepackage{calc}
\makeatletter

\IfFileExists{footnotehyper.sty}{
    \usepackage{footnotehyper }
}{
    \usepackage{footnote}
}

\makesavenoteenv{longtable}
\usepackage{bookmark}

% Document metadata
\hypersetup{
    hidelinks,
    pdftitle={Mina Hermina's Resume},
    pdfauthor={Mina Hermina},
    pdfsubject={Resume},
    pdfcreator={LaTeX},
    pdfproducer={pdfTeX},
    pdfkeywords={resume, CV}
}

\begin{document}

% -----------------------------------
% Info section
% -----------------------------------
\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 2\tabcolsep) * \real{0.9824}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 2\tabcolsep) * \real{0.0176}}@{}}
\textbf{\LARGE{Mina Albert Saeed Hermina}}
\vspace{1pt} \\ 
Phone: +20 1272937424

mina.albert.saeed@gmail.com

linkedin.com/in/minaalbert

github.com/minahermina

Egypt & \\
\end{longtable}
\vspace{-10pt}

% -----------------------------------
% Summary section
% -----------------------------------
\textbf{SUMMARY}
\vspace{-8pt}
\nopagebreak[4]
\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 0\tabcolsep) * \real{1.0000}}@{}}
\toprule
\vspace{0pt}
    A motivated computer science student specializing in IT, with a strong passion for GNU/Linux, networks, and operating systems. Enthusiastic about their evolution from inception to the present, I am eager to apply my knowledge in real-world projects. Seeking an internship in \textbf{Linux/Unix Systems Engineering or Programming} to contribute my skills while gaining hands-on experience.
\end{longtable}
\vspace{-8pt}

% -----------------------------------
% Extracurriculars section
% -----------------------------------
\textbf{EXTRACURRICULARS}
\vspace{-7pt}
\nopagebreak[4]
\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 0\tabcolsep) * \real{1.0000}}@{} }
\toprule\noalign{}
\vspace{0pt}
    \begin{minipage}[t]{\linewidth}\raggedright
        \textbf{IEEE Cairo University Student Branch}
        \hspace{27em}\textbf{March 2024 -- June 2024} \\
        Networks Instructor
        \vspace{.05em}
        \begin{itemize}
            \item
              Contributing to the development of technical content for the committee
              sessions and instructed real sessions for network committee members
        \end{itemize}
    \end{minipage} \\
\end{longtable}
\vspace{-10pt}

% -----------------------------------
% SKILLS \& LANGUAGES
% -----------------------------------
\textbf{SKILLS \& LANGUAGES}
\vspace{-8pt}
\nopagebreak[4]
\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 0\tabcolsep) * \real{1.0000}}@{}}
\toprule\noalign{}
\vspace{0pt}
\begin{minipage}[t]{\linewidth}\raggedright
    \textbf{Technical skills \& TOOLS:}
    \begin{itemize}
        \item
          Python, C, C++, Java, OOP \& Data structures
        \item
          POSIX-compliant shell scripting and Bash
        \item
          GNU/Linux
        \item
          Basic understanding of TCP/IP Protocols Suite
        \item
          Git, GitHub, vim, tmux
    \end{itemize}

    \textbf{Languages:}
    \begin{itemize}
        \item
          Arabic: Native proficiency
        \item
          English: Intermediate proficiency (B1)
    \end{itemize}
\end{minipage} \\
\end{longtable}
\vspace{-10pt}

% -----------------------------------
% Projects
% -----------------------------------
\textbf{PROJECTS}
\vspace{-8pt}
\nopagebreak[4]
\begin{longtable}[]{@{}
    >{\raggedright\arraybackslash}p{(\columnwidth - 2\tabcolsep) * \real{0.7}}
    >{\raggedleft\arraybackslash}p{(\columnwidth - 2\tabcolsep) * \real{0.3}}@{}}
\toprule
\vspace{0pt}
\endhead

\textbf{Linux Kernel With lockdep} & \textbf{April 2024} \\
\multicolumn{2}{p{\linewidth}}{
\vspace{-6pt}
        \begin{itemize}
            \item
              Configured and built the Linux kernel to enable lockdep module which
                helps in debugging \newline{} deadlocks in kernel space, replacing the new
              custom kernel into my system and using it.
        \end{itemize}
}\\[-5pt]

\textbf{imglib} & \textbf{November 2024 -- December 2024} \\
\multicolumn{2}{p{\linewidth}}{
\vspace{-6pt}
    \begin{itemize}
        \item 
            Developed a lightweight, portable C library for image manipulation on Unix-like systems.
        \item 
            Followed the Suckless C coding style and wrote a portable Makefile, avoiding GNU-specific extensions.

        \item 
            Implemented efficient pixel access using stride-based indexing for performance optimization.
    \end{itemize}
}\\[-5pt]

\textbf{POSIX Compliant Shell scripts Creation} & \textbf{September 2023 - Current} \\
\multicolumn{2}{p{\linewidth}}{
\vspace{-6pt}
    \begin{itemize}
        \item
          Building POSIX-compliant shell scripts to automate daily tasks on my
            system like spinning up a \newline{} virtual machine, unarchiving archive files
          and screen casting.
    \end{itemize}
}\\[-5pt]


    \textbf{Higher Studies Systems} & \textbf{May 2023 -- July 2023} \\
\multicolumn{2}{p{\linewidth}}{%
\vspace{-6pt}
    \begin{itemize}
        \item
          Building a user-friendly website using \textbf{Django} framework for
            the students and staff of Higher \newline{} studies to streamline the education
          process.
        \item
          Separated student and admin roles by creating distinct models,
            ensuring tailored access to \newline{} specific pages using Django decorators
          for each user type.
    \end{itemize}
}
\end{longtable}
\vspace{-12pt}

% -----------------------------------
% EDUCATION
% -----------------------------------
\textbf{EDUCATION}
\vspace{-8pt}
\begin{longtable}[]{@{}
    >{\raggedright\arraybackslash}p{(\columnwidth - 0\tabcolsep) * \real{1.0000}}@{}}
\toprule\noalign{}
\vspace{0pt}
\begin{minipage}[t]{\linewidth}\raggedright
Faculty of Computers and Artificial Intelligence, IT Department, Cairo
    university.
\hspace{10em}\textbf{October 2024 -- Current}

    \begin{itemize}
        \item
          Bachelor's Degree in Information Technology (GPA: 3.2)
        \end{itemize}
\end{minipage} \\
\end{longtable}

% \newpage

% -----------------------------------
% CERTIFICATES
% -----------------------------------
\textbf{CERTIFICATES}
\vspace{-8pt}
\begin{longtable}[]{@{}
    >{\raggedright\arraybackslash}p{(\columnwidth - 0\tabcolsep) * \real{1.0000}}@{}}
\toprule\noalign{}
\vspace{0pt}
\begin{minipage}[t]{\linewidth}\raggedright
    \begin{itemize}
        \item
            CCNA: Introduction to Networks
            \hspace{28em}\textbf{July 2024 -- August 2024}
        \item
            CCNA: Switching, Routing, and Wireless Essentials
            \hspace{20.3em}\textbf{July 2024 -- August 2024}
        \end{itemize}
\end{minipage} \\
\end{longtable}

\end{document}
